Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Typo
Emphasise partial nature of array term interpretation

\begin{defn}[Neighbourhood index]
\label{def:neighbour}
  For an array subscript $a(\bar{e})$ an index $e \in \bar{e}$ is a
  \emph{neighbourhood index} if $e$ is of the form $e \equiv i$, $e \equiv i +
  c$, or $e \equiv i - c$, where $c$ is an integer constant. That is, a
  neighbourhood index is a constant translation of an induction variable. (The
  relation $\equiv$ identifies terms up-to commutativity of $+$ and the inverse
  relationship of $+$ and $-$ \eg{}, $(-b) + i \equiv i - b$).
\end{defn}

@@

\begin{defn}
  Recall array subscript terms of the form $a(\bar{e})$ from
  \Cref{defarray-subs}. We interpret these terms with
  $\interp{-}^{\mathit{aexp}} : \textit{array-exp} \to \mathcal{P}(\bz{})^N$.
%
  \begin{align*}
    \interp{a(\bar{e})}^{\mathit{aexp}} =
      \prod_{1 \leq i \leq N} \mathit{subscript}(\bar{e}_i) & &
  %
    \textit{subscript}(e) = \begin{cases}
      \{ c \} & e \equiv i \pm c \\
      \bz & e \; \mbox{is constant}
    \end{cases}
  \end{align*}
\end{defn}

>>>>

\begin{defn}[Neighbourhood index]\label{def:neighbour-ix}
  For an array subscript $a(\bar{e})$ an index $e \in \bar{e}$ is a
  \emph{neighbourhood index} if $e$ is of the form $e \equiv i$, $e \equiv i +
  c$, or $e \equiv i - c$, where $c$ is an integer constant. That is, a
  neighbourhood index is a constant translation of an induction variable. (The
  relation $\equiv$ identifies terms up-to commutativity of $+$ and the inverse
  relationship of $+$ and $-$ \eg{}, $(-b) + i \equiv i - b$).
\end{defn}

@@

\begin{defn}
  Recall array subscript terms of the form $a(\bar{e})$ from
  \Cref{def:array-subs}. We interpret these terms with the partial
  interpretation $\interp{-}^{\mathit{aterm}} : \textit{array-term}
  \prightarrow{} \mathcal{P}(\bz{})^N$. The interpretation is defined when
  all indices are either constant or neighbourhood indices as defined in
  \Cref{def:neighbour-ix}.
%
  \begin{align*}
    \interp{a(\bar{e})}^{\mathit{aterm}} =
      \prod_{1 \leq i \leq N} \mathit{subscript}(\bar{e}_i) & &
  %
    \textit{subscript}(e) = \begin{cases}
      \{ c \} & e \equiv i \pm c \\
      \bz & e \; \mbox{is constant}
    \end{cases}
  \end{align*}
\end{defn}
